| Early stopping in clinical PET studies: \n| how to reduce expense and exposure

### 2020-09-18 ArticleDraft/Draft.Rmd
Updated docs for main simulation script

\begin{figure}
        \centering
        \includegraphics[width=140mm]{/Users/pontus.sigray/Github/Early_stopping_in_PET/Results/Figures/Figure6.png}
        \caption{\textit{Sequential BF testing applied to real PET data. Patients with major depressive disorder were compared to healthy control subjects using $[^{11}$C]WAY100635 BP\textsubscript{F} as a measure of 5HT1A receptor availability in the raphe nuclei. BF testing starts after $12$ subjects/group have been collected and a stop decision is triggered at $27$ subjects/group. The blue line denotes the stopping threshold for H\textsubscript{1} (set to $5$) and the red line the stopping threshold for H\textsubscript{0} (set to $\nicefrac{1}{5}$). The black line shows the change in BF following the inclusion of each additional patient-control pair. The grey line shows how the BF trajectory would have looked, assuming no stopping decision was made, and the data collection instead continued up until the full sample of $40$ subjects/group.}}
          \label{fig_seqWAY}
\end{figure}

@@

[^fn3]: The Bayes Factor is also known as the “predictive updating factor” of Bayes Theorem. It is what updates the prior odds of two competing hypotheses into posterior odds after seeing the observed data, and hence describes the relative “predictive adequacy” of the hypotheses.  Assuming that H~0~ and H~1~ have equal prior probability (P(H~1~) = P(H~0~) = 0.5), then a BF of 4 means that after conducting the study, H~1~ is 4 times more likely than H~0~. This corresponds to a posterior probability of 75% for H~1~ and 25% for H~0~ (@Kass1995). Although posterior odds are the natural extension of the BF, researchers tend to only report the BF as a stand-alone metric for assessing different hypotheses, due to the inherent subjective nature of specifying prior odds.  \newline \phantom{x}

>>>>

\begin{figure}
        \centering
        \includegraphics[width=140mm]{/Users/pontus.sigray/Github/Early_stopping_in_PET/Results/Figures/Figure6.png}
        \caption{\textit{Sequential BF testing applied to real PET data. Patients with major depressive disorder were compared to healthy control subjects using $\it{[^{11}C]}$WAY100635 BP\textsubscript{F} as a measure of 5HT1A receptor availability in the raphe nuclei. BF testing starts after $12$ subjects/group have been collected and a stop decision is triggered at $27$ subjects/group. The blue line denotes the stopping threshold for H\textsubscript{1} (set to $5$) and the red line the stopping threshold for H\textsubscript{0} (set to $\nicefrac{1}{5}$). The black line shows the change in BF following the inclusion of each additional patient-control pair. The grey line shows how the BF trajectory would have looked, assuming no stopping decision was made, and the data collection instead continued up until the full sample of $40$ subjects/group.}}
          \label{fig_seqWAY}
\end{figure}

@@

[^fn3]: The Bayes Factor is also known as the “predictive updating factor” of Bayes Theorem. It is what updates the prior odds of two competing hypotheses into posterior odds after seeing the observed data, and hence describes the relative “predictive adequacy” of the hypotheses.  Assuming that H~0~ and H~1~ have equal prior probability (P(H~1~) = P(H~0~) = 0.5), then a BF of 4 means that after conducting the study, H~1~ is 4 times more likely than H~0~. This corresponds to a posterior probability of 75% for H~1~ and 25% for H~0~ [@Kass1995]. Although posterior odds are the natural extension of the BF, researchers tend to only report the BF as a stand-alone metric for assessing different hypotheses, due to the inherent subjective nature of specifying prior odds.  \newline \phantom{x}
